---
title: "Data Missingness Report"
output: html_notebook
---

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

```{r Setup, include=FALSE}
#setwd("~/Documents/DepenD Lab/NeuroMAP/NMAPReports/") #may need to change for each person running report

directory_onedriveH<-file.path("/Users/strength/OneDrive - The Pennsylvania State University/") #set personal directory
directory_onedriveW<-file.path("/Users/bbh5255/OneDrive - The Pennsylvania State University/") #set personal directory
directory_work<-file.path("/Users/bbh5255/Documents/DepenD Lab/NeuroMAP/NMAPReports/") #set directory
directory_home<-file.path("/Users/strength/Documents/DepenD Lab/NeuroMAP/NMAPReports/") #set directory

if (!require(easypackages)) {install.packages("easypackages"); library(easypackages) }
packages("readxl", "tidyverse", "dbplyr", "tidyr", "qualtRics", "lubridate", "dataCompareR", "kableExtra")

q_token <- "bigsHycE1tmf2sfK5HR2CKShxGPasXZqC2QZ2Gvl" #enter qualtrics API Token
qualtrics_api_credentials(api_key = q_token, 
                          base_url = "pennstate.ca1.qualtrics.com",
                          install = TRUE, overwrite = TRUE)

TodayDate <- today()
TodayPlus7 <-TodayDate +7

```


```{r Import Qualtrics Data, message=TRUE, include=FALSE}
surveys<-all_surveys()
S1Report <-fetch_survey(surveyID = "SV_23S2sjLm5Lmq7Ah", label = TRUE, verbose = TRUE, convert = FALSE, force_request = TRUE)
S2Report <-fetch_survey(surveyID = "SV_8jJlCrM3V7m0BoN", label = TRUE, verbose = TRUE, convert = FALSE, force_request = TRUE)
S3Report<-fetch_survey(surveyID = "SV_8ixbUxRgNWtxuHH", label=TRUE, verbose = TRUE, convert = FALSE, force_request = TRUE)
S4Report <-fetch_survey(surveyID = "SV_8tOIVRgh1T4D2g5",  label = TRUE, verbose = TRUE, convert = FALSE, force_request = TRUE) 
#convert date to ddtm readable format in R

#S3Report$s3_sessioninfo_1_TEXT<-lubridate::mdy(S3Report$s3_sessioninfo_1_TEXT)
#S4Report$s4_sessioninfo_1_TEXT<-lubridate::mdy(S4Report$s4_sessioninfo_1_TEXT)

```

```{r Clean S1Report Qualtrics Data}
S1Report<-S1Report %>%
  rename(
    
  )

```

```{r Clean Tracker Data}
Tracker <- read_xlsx(paste0(directory_onedriveW, "NEUROMAP Master V2.xlsx"), sheet = "Tracker")

Tracker <- Tracker %>%
  select(ID,
         EMAIL,
         PHONE,
         FIRSTNAME,
         LASTNAME,
         `STUDY PROGRESS`
         ) %>%
 rename(`Email` = "EMAIL") 

```

```{r Cleaning Acuity Scheduling Data, include=FALSE}
Acuity <-read_csv(paste0(directory_work, "Acuity Session Reports/all participant_acuity_feb20th.csv")) #read in Acuity Acuity info

LastWeek<-TodayDate - 7

#convert date time to readable format in R
Acuity$`Start Time (AM/PM)`<-format(strptime(Acuity$`Start Time`, format= '%m/%d/%y %H:%M'), "'%m/%d/%y '%I:%M:%S %p'") #convert time to am/pm from 24 hour clock
Acuity$`Start Time`<-lubridate::mdy_hm(Acuity$`Start Time`) #convert time to R friendly format
Acuity$`Session Date`<- date(Acuity$`Start Time`) # create date only variable for searching purposes

Acuity<-Acuity %>%
  mutate(`Type (Recode)`=case_when(
    .$`Type` == "Session 1" ~ "Session 1",
    .$`Type` == "Session 1 Follow Up (1.5 hours)" ~ "Session 1 FU",
    .$`Type` == "Session 1 Follow Up (30 minutes)" ~ "Session 1 FU",
    .$`Type` == "Session 1 Follow Up (3 hours)" ~ "Session 1 FU",
    .$`Type` == "Session 2 (Marissa)" ~ "Session 2",
    .$`Type` == "Session 2 (Mia)" ~ "Session 2",
    .$`Type` == "Session 2 (Austin)" ~ "Session 2",
    .$`Type` == "Session 2 (Grace)" ~ "Session 2",
    .$`Type` == "Session 2 (Chloe)" ~ "Session 2",
    .$`Type` == "Session 2 (Daniel and Begonia)" ~ "Session 2",
    .$`Type` == "Session 3 (1 hour follow-up)" ~ "Session 3 FU",
    .$`Type` == "Session 3 Follow-Up  (1.5 Hours)" ~"Session 3 FU",
    .$`Type` == "Session 3" ~ "Session 3",
    .$`Type` == "SONA Study 1" ~ "Other",
    .$`Type` == "RA Interviews" ~ "Other"
    )) %>%
  select(-c(`Appointment Price`,
         `Amount Paid Online`,
         `Certificate Code`,
         `Date Scheduled`,
         `Label`,
         `Appointment ID`,
         `Notes`,
         `Paid?`,
         `Scheduled By`)) %>%
  dplyr::filter(`Type (Recode)` != "Other") %>%
  #spread(key = `Type (Recode)`, value = `Session Date`) %>%
  gather(
    `Session 1 FU`)
  

ParticipantData<-dplyr::full_join(Acuity, Tracker, by = "Email")

View(ParticipantData)
```



```{r Filter Current Weeks Session}

ParticipantData %>% 
  select(
    `ID`,
   # `First Name`,
   # `Last Name`,
    `Email`,
    `Canceled`,
    `Type`,
    `Session Date`) %>%
  filter(`Session Date`>= LastWeek & `Session Date`<= TodayDate) %>%
  arrange(ID) %>%
  kable(format = "html", escape = F, caption = "Record of Sessions")

```


```{r}
Tracker %>%
  select(
    `ID`,
    `NAME`,
    `ACTUAL GROUP`,
    `STUDY PROGRESS`,
    `NOTES ABOUT STATUS`,
    `Email`
  ) %>%
  filter(`STUDY PROGRESS` == "IN PROG") %>%
  #full_join(Acuity, Tracker, by = `Email`) %>%
  kable(format = "html", escape = F, caption = "In Progress Participants")

```



```{r}

Tracker %>%
  select(
    `ID`,
    `NAME`,
    `ACTUAL GROUP`,
    `STUDY PROGRESS`,
    `NOTES ABOUT STATUS`,
    `Email`,
    `S4 DATE`,
    `DAYS BETWEEN BASELINE AND S4`,
    `NOTES`
  ) %>%
  filter(`S4 DATE`>= TodayDate & `S4 DATE`<= TodayPlus7) %>%
  mutate(
   `MONTHS SINCE BASELINE` = `DAYS BETWEEN BASELINE AND S4`/ 30)
  #full_join(Acuity, Tracker, by = `Email`) %>%
  kable(format = "html", escape = F, caption = "S4's in Next 7 Days")
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

