---
title: "Weekly Recruitment Check"
subtitle: 
author: 
date: 2/13/2020
output:
  html_document:
    code_folding: hide
    df_print: kable
    mathjax: default
    number_sections: no
    theme: spacelab
    toc: yes
    toc_depth: 3
    fig_width: 9 
    fig_height: 6 
  pdf_document:
    code_folding: hide
    df_print: kable
    number_sections: yes
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(cowplot)
library(qualtRics)
library(readxl)
#library(skimr)
library(tidyverse)
library(lubridate)
library(RColorBrewer)
library(kableExtra)

START_WEEK <- mdy("02/07/2020") #only change me, set as date of neuromap Startup meeting - 7 days
GY <- 1 #year of grant, change ?
RO1_TABLE_CAPTION <- "February R01 Enrollment Targets"
RO1_TOTAL_CAPTION <- "Cummulative R01 Enrollment To Date (Aug 2019 - Feb 2020)"
ENROLL_PASTWEEK_TITLE<- "Activity from Past Week (Feb 7th - Feb 13th)" 
```


```{r Import + Clean Data for Enrollment Master, include=FALSE}
#setwd("Box/DEPENd/NeuroMAP/Recruitment/Participant Management/")
directory_onedriveH<-file.path("/Users/strength/OneDrive - The Pennsylvania State University/") #set personal directory
directory_onedriveW<-file.path("/Users/bbh5255/OneDrive - The Pennsylvania State University/") #set personal directory
directory_work<-file.path("/Users/bbh5255/Box/DEPENd/NeuroMAP/Recruitment/Participant Management/") #set directory
directory_home<-file.path("/Users/strength/Box/DEPENd/NeuroMAP/Recruitment/Participant Management/") #set directory


#read in data for master file spreadsheet and R01 information - REMOVE PASSWORD FROM MASTER
MASTER <- read_xlsx(paste0(directory_onedriveW, "NEUROMAP Master V2.xlsx"), sheet = "MasterData")
ENROLL_OVERVIEW <- read_xlsx(paste0(directory_onedriveW, "NEUROMAP Master V2.xlsx"), sheet = "RO1 Aggregate", col_names = TRUE)
TRACKER <- read_xlsx(paste0(directory_onedriveW, "NEUROMAP Master V2.xlsx"), sheet = "Tracker")


#tidy up column names for MASTER

MASTER<-dplyr::rename(MASTER, SCREEN_SENTDATE = "SCREEN: SENT DATE", SCREEN_COMPLETEDATE = "SCREEN: COMPLETE DATE", SCREEN_COMPLETEYN = "SCREEN: COMPLETE Y/N", INEL_CODE = "INELEGIBILITY CODE", INEL_PHASE ="PHASE DEEMED INELIGIBLE", INEL_YN = "ELIGIBLE YN")

#create record of start month and year for participants
MASTER$SCREEN_SENTDATE <- as.POSIXct(strptime(MASTER$SCREEN_SENTDATE, format = '%Y-%m-%d'))
MASTER$SCREEN_COMPLETEDATE <- as.POSIXct(strptime(MASTER$SCREEN_COMPLETEDATE, format = '%Y-%m-%d'))
#MASTER$S1_DATE <- as.POSIXct(strptime(MASTER$S1_DATE, format = '%Y-%m-%d'))

MASTER$SCREEN_SENT_MONTH <- format(MASTER$SCREEN_SENTDATE, '%m')
MASTER$SCREEN_SENT_YEAR <- format(MASTER$SCREEN_SENTDATE, '%Y')

MASTER$SCREEN_COMPLETE_MONTH <- format(MASTER$SCREEN_COMPLETEDATE, '%m')
MASTER$SCREEN_COMPLETE_YEAR <- format(MASTER$SCREEN_COMPLETEDATE, '%Y')

#MASTER$S1_MONTH <- format(MASTER$S1_DATE, '%m')
#MASTER$S1_YEAR <- format(MASTER$SCREEN_COMPLETEDATE, '%Y')

#factorize source

MASTER$STATUS <-factor(MASTER$STATUS, levels = c("Completed S2", "Completed screen", "Inquiry", "Invited S1", "No longer interested", "Scheduled S1", "Screen sent"))
levels(MASTER$STATUS)[levels(MASTER$STATUS)=="Screen sent"] <- "Screen Sent, Not Completed"
levels(MASTER$STATUS)[levels(MASTER$STATUS)=="Completed screen"] <- "Ineligible After Screen"

# MASTER$SOURCE <- factor(MASTER$SOURCE, levels = c("Craigslist", "Facebook/Contact Form", "Flyer", "Flyer/Davey Lab", "Flyer/HUB", "Flyer/Library", "Flyer/Moore", "Flyer/On Campus", "Flyer/Willard", "Flyer/Forum Building", "StudyFinder", "Word of Mouth", "Unknown"))
MASTER$SOURCE[is.na(MASTER$SOURCE)] <- "Unknown"

#clean variables in enrollment master
TRACKER <- TRACKER %>% rename(S1_DATE = "S1 DATE", S2_DATE = "S2 DATE", S3_DATE = "S3 DATE", S4_DATE = "S4 DATE", S5_DATE = "S5 DATE", R01_ENROLLMENT = "FMRI GROUP (Y/N)", STATUS = "NOTES ABOUT STATUS")

MASTER$NAME<-gsub("(?<=[A-Z])[^A-Z]+", "", MASTER$NAME, perl = TRUE) # remove names and make initials
TRACKER$NAME<-gsub("(?<=[A-Z])[^A-Z]+", "", TRACKER$NAME, perl = TRUE) # remove names and make initials TRACKER

TRACKER$`S1 FU 1`<- as_date(TRACKER$`S1 FU 1`)

#code for establishing the day of report for the study
START_LWEEK <-START_WEEK - days (7) 
END_WEEK <-START_WEEK + days(7) 
END_NWEEK <- END_WEEK +days (7)

CURRENT_MONTH_GRANT<- month(START_WEEK - months(3)) #month of study (do not change)


#code for subsetting only actual entries in Master tab
```


```{r Cleaning Acuity Scheduling Data, include=FALSE}
SCHEDULE <-read_csv(paste0(directory_work, "Acuity Session Reports/schedule2020-02-13.csv")) #read in acuity schedule info

#convert date time to readable format in R
SCHEDULE$`Start Time (AM/PM)`<-format(strptime(SCHEDULE$`Start Time`, format= '%m/%d/%y %H:%M'), "'%m/%d/%y '%I:%M:%S %p'") #convert time to am/pm from 24 hour clock
SCHEDULE$`Start Time`<-lubridate::mdy_hm(SCHEDULE$`Start Time`) #convert time to R friendly format
SCHEDULE$`Session Date`<- date(SCHEDULE$`Start Time`) # create date only variable for searching purposes

SCHEDULE$Type


SCHEDULE<-SCHEDULE %>%
  mutate(`Type (Recode)`=case_when(
    .$`Type` == "Session 1" ~ "Session 1",
    .$`Type` == "Session 1 Follow Up (1.5 hours)" ~ "Session 1 FU",
    .$`Type` == "Session 2 (Marissa)" ~ "Session 2",
    .$`Type` == "Session 2 (Mia)" ~ "Session 2",
    .$`Type` == "Session 2 (Austin)" ~ "Session 2",
    .$`Type` == "Session 2 (Daniel and Begonia)" ~ "Session 2",
    .$`Type` == "Session 3 (1 hour follow-up)" ~ "Session 3 FU",
    .$`Type` == "Session 3 Follow-Up  (1.5 Hours)" ~"Session 3 FU",
    .$`Type` == "Session 3" ~ "Session 3"
    ))

```

```{r eval=FALSE, include=FALSE}
q_token <- "bigsHycE1tmf2sfK5HR2CKShxGPasXZqC2QZ2Gvl" #Begonias Account
qualtrics_api_credentials(api_key = q_token, 
                          base_url = "pennstate.ca1.qualtrics.com",
                          install = TRUE, overwrite = FALSE)
```


```{r Import Qualtrics Data, message=TRUE, include=FALSE}
surveys<-all_surveys()
S3_Report<-fetch_survey(surveyID = "SV_8ixbUxRgNWtxuHH", label=TRUE, verbose = TRUE, convert = FALSE, force_request = TRUE)
S4_Report <-fetch_survey(surveyID = "SV_8tOIVRgh1T4D2g5",  label = TRUE, verbose = TRUE, convert = FALSE, force_request = TRUE) 
#convert date to ddtm readable format in R
S3_Report$s3_sessioninfo_1_TEXT<-lubridate::mdy(S3_Report$s3_sessioninfo_1_TEXT)
S4_Report$s4_sessioninfo_1_TEXT<-lubridate::mdy(S4_Report$s4_sessioninfo_1_TEXT)
```

******
# Session Reports
******
## *Session 3*

### Session 3 Overview

```{r Session 3 Report Ratings, echo=FALSE}
S3_Report %>% 
  select(s3_sessioninfo_1_TEXT, 
         s3_sessioninfo_4_TEXT, 
         s3_sessioninfo_3_TEXT, 
         s3overall_score_1, 
         s3section_score_1_TEXT, 
         s3section_score_2_TEXT, 
         s3section_score_3_TEXT, 
         s3section_score_4_TEXT, 
         s3section_score_5_TEXT, 
         s3section_score_6_TEXT, 
         s3section_score_8_TEXT
         ) %>%
  #mutate(`s3overall_score_1` = cell_spec(`s3overall_score_1`, "html", color = ifelse(s3overall_score_1 > 3, "green", "red"))) %>%
  rename(`Date` = s3_sessioninfo_1_TEXT,
         `ID` = s3_sessioninfo_4_TEXT,
         `Researcher` = s3_sessioninfo_3_TEXT,
         `Overall Rating` = s3overall_score_1,
         `Physio Rating`= s3section_score_1_TEXT,
         `EyeTraking Rating` = s3section_score_2_TEXT,
         `Vanilla Baseline Rating`= s3section_score_3_TEXT,
         `Mushrooms Rating` = s3section_score_4_TEXT,
         `DTK Rating` = s3section_score_5_TEXT,
         `Vending Machine Rating` = s3section_score_6_TEXT,
         `Neighborhood Rating` = s3section_score_8_TEXT) %>%
  dplyr::filter((.$Date>= START_WEEK & .$Date <= END_WEEK)) %>%
  arrange(`Overall Rating`) %>%
  kable(format = "html", escape = F, caption = "Session 3 Ratings") %>%
  kable_styling(bootstrap_options = "condensed", full_width = F) %>%
  footnote(
  general = "1 = serious issues with data, i.e. participant found out their parent was ill during the session, all the tasks failed, participant was asleep etc. 
    2 = 40-60 % of the data/session had problems
    3 = A couple of small problems but overall good
    4 = One small problem 
    5 = Don't need to talk about it :) Session was perfect!",
  general_title = "Overall Rating Scale",
  footnote_as_chunk = F, title_format = c('italic', "underline")) %>%
  scroll_box(width = "100%", height = "300px")
```
******
### Session 3 Detailed Reports
******

```{r Session 3 Detailed Reports (ET, Physio Only), echo=FALSE}
S3_Report %>% 
  select(
    s3_sessioninfo_1_TEXT, 
    s3_sessioninfo_4_TEXT, 
    s3_sessioninfo_3_TEXT,
    s3physio_notes, 
    s3eyetraking_notes,
    ) %>%
  rename(
    Date = s3_sessioninfo_1_TEXT,
    ID = s3_sessioninfo_4_TEXT,
    `RA` = s3_sessioninfo_3_TEXT,
    `Physio Notes` = s3physio_notes,
    `EyeTraking Notes` = s3eyetraking_notes,
    ) %>%
  #drop_na() %>%
  dplyr::filter((.$Date>= START_WEEK & .$Date <= END_WEEK)) %>%
  kable() %>%
  #add_header_above(header = "Header Formating") %>%
  kable_styling(full_width = F, fixed_thead = T) %>%
  column_spec(column = 1, width = "7em; display: inline-block;") %>%
  column_spec(column = 3, border_right = T) %>%
  column_spec(column = 4, width = " 15em") %>%
  scroll_box(width = "100%", height = "500px")

```

******

``` {r Session 3 Detailed Reports (Tasks), echo = FALSE }
S3_Report %>% 
  select(
    s3_sessioninfo_1_TEXT, 
    s3_sessioninfo_4_TEXT, 
    s3_sessioninfo_3_TEXT,
    s3mushroom_notes, 
    s3dtk_notes,
    s3neighborhood_notes,
    s3vm_notes,
    ) %>%
  rename(
    Date = s3_sessioninfo_1_TEXT,
    ID = s3_sessioninfo_4_TEXT,
    `RA` = s3_sessioninfo_3_TEXT,
    `DTK Notes` = s3dtk_notes,
    `Neighborhood Notes` = s3neighborhood_notes,
    `Mushroom Notes` = s3mushroom_notes,
    `Vending Machine Notes` = s3vm_notes,
    ) %>%
  #drop_na() %>%
  dplyr::filter((.$Date>= START_WEEK & .$Date <= END_WEEK)) %>%
  kable() %>%
  kable_styling(full_width = F, fixed_thead = T) %>%
  column_spec(column = 1, width = "7em; display: inline-block;") %>%
  column_spec(column = 3, border_right = T) %>%
  scroll_box(width = "100%", height = "500px") 

```



## *Session 4*

### Session 4 Overview

```{r Session 4 Report Ratings, echo=FALSE}
S4_Report %>% 
  select(s4_sessioninfo_1_TEXT, 
         s4_sessioninfo_4_TEXT, 
         s4_sessioninfo_3_TEXT, 
         s4overall_score_1, 
         s4section_score_1_TEXT, 
         s4section_score_2_TEXT, 
         s4section_score_3_TEXT, 
         s4section_score_4_TEXT, 
         s4section_score_5_TEXT, 
         s4section_score_6_TEXT, 
         s4section_score_7_TEXT,
         s4section_score_8_TEXT,
         s4section_score_9_TEXT
         ) %>%
  rename(`Date` = s4_sessioninfo_1_TEXT,
         `ID` = s4_sessioninfo_4_TEXT,
         `Researcher` = s4_sessioninfo_3_TEXT,
         `Overall Rating` = s4overall_score_1,
         `Physio Rating`= s4section_score_1_TEXT,
         `EyeTraking Rating` = s4section_score_2_TEXT,
         `Pre Scan Prep Rating`= s4section_score_3_TEXT,
         `Localizer/Structural/Pre-Resting State Rating` = s4section_score_4_TEXT,
         `Pav Rating` = s4section_score_5_TEXT,
         `Instrumental Rating` = s4section_score_6_TEXT,
         `PIT Rating` = s4section_score_7_TEXT,
         `Post Resting State Scan` = s4section_score_8_TEXT,
          `Transfer Task/Data Transfer` = s4section_score_9_TEXT
          ) %>%
  dplyr::filter((.$Date>= START_WEEK & .$Date <= END_WEEK)) %>%
  arrange(`Overall Rating`) %>%
  kable(format = "html", escape = F, caption = "Session 4 Ratings") %>%
  kable_styling(bootstrap_options = "condensed", full_width = F) %>%
  footnote(
  general = "1 = serious issues with data, i.e. participant found out their parent was ill during the session, all the tasks failed, participant was asleep etc. 
    2 = 40-60 % of the data/session had problems
    3 = A couple of small problems but overall good
    4 = One small problem 
    5 = Don't need to talk about it :) Session was perfect!",
  general_title = "Overall Rating Scale",
  footnote_as_chunk = F, title_format = c('italic', "underline")) %>%
  scroll_box(width = "100%", height = "300px")
```
    
  )
```


# Enrollment Overview

## RO1 Enrollment Targets For January


```{r R01 Enrollment Overview, echo=FALSE}

#Totals for the month

R01_OVERVIEW <-ENROLL_OVERVIEW %>%
  select(
    YEAR,
    MONTH,
    GROUP,
    EXPECTED,
    PROJECTED,
    `STATUS TBD`,
    `ENROLLED FMRI`,
    `ENROLLED NO FMRI`,
    `EXCLUDED`,
    C_EXPECTED
    ) %>%
  filter(MONTH == CURRENT_MONTH_GRANT & YEAR == GY) 

OVERVIEW_TABLE <-R01_OVERVIEW %>%
  select(GROUP, EXPECTED, PROJECTED, `ENROLLED FMRI`, `ENROLLED NO FMRI`, `STATUS TBD`, `EXCLUDED` )

knitr::kable(
  OVERVIEW_TABLE, 
  caption = RO1_TABLE_CAPTION,
  col.names = c("Diagnostic Group", "Expected Enrollment to Fulfill R01 Timeline in the Month of February", "In Process of Enrollment", "Enrolled in FMRI Group", "Not Enrolled in FMRI Group", "Status TBD", "Excluded"))
```

*****

```{r echo=FALSE}
#TOTAL TO DATE

RO1_TOTAL <-ENROLL_OVERVIEW %>%
  #select(YEAR, MONTH, GROUP,  C_EXPECTED, `C_ENROLLED FMRI`,`C_ENROLLED NO FMRI`,C_EXCLUDED,C_PROJECTED ) %>%
    dplyr::filter(MONTH == CURRENT_MONTH_GRANT & YEAR) %>%
  group_by(GROUP)

RO1_TOTAL <-select(RO1_TOTAL, GROUP, C_EXPECTED, `C_ENROLLED FMRI`, C_PROJECTED, `C_TBD`, `C_ENROLLED NO FMRI`, C_EXCLUDED)

knitr::kable(
  RO1_TOTAL,
  caption = RO1_TOTAL_CAPTION,
  col.names = c("Diagnostic Group", "Cumulative Expected Enrollment to Fulfill R01 Timeline", "Total Enrolled in FMRI Group", "Total In Process of Enrollment", "Total Status TBD", "Total Not Enrolled in FMRI Group", "Excluded"))

```

*****
## Visual of Study Progress

```{r Distribution of Sessions, echo=FALSE}

a<-SCHEDULE %>% select(
  `Start Time (AM/PM)`,
  `Session Date`,
  `Canceled`,
  `Type`,
  `Type (Recode)`) %>% 
  dplyr::filter((.$`Session Date`>= START_WEEK & .$`Session Date`<= END_WEEK) & is.na(.$Canceled)) %>%
  group_by(`Type (Recode)`) %>%
  ggplot(aes(x=`Type (Recode)`)) +
  geom_bar(stat="count") +
  labs(title ="Distribution of Scheduled S1-S3 (Past 7 Days)", y = "Count", x = "Session Number")
  
 
b<-SCHEDULE %>% select(
  `Start Time (AM/PM)`,
  `Session Date`,
  `Canceled`,
  `Type`,
  `Type (Recode)`) %>% 
  dplyr::filter((.$`Session Date`>= END_WEEK) & is.na(.$Canceled)) %>%
  ggplot(aes(x=`Type (Recode)`)) +
  geom_bar(stat="count") +
  labs(title ="Distribution of all Upcoming Scheduled S1-S3", y = "Count", x = "Session Number")

c <-TRACKER %>% select('STUDY PROGRESS') %>%
  dplyr::filter(!`STUDY PROGRESS` %in% c("MIA", "NOT ENROLLED - MISSED S1", "INEL", "STUCK S3")) %>%
  ggplot(aes(x=`STUDY PROGRESS`)) +
  geom_bar(stat="count") +
  labs(title ="Distribution of Overall Participant Status", y = "Count", x = "Status")

  
  plot_grid(a, b,c, nrow = 3)


```

*****
## Time Series

```{r echo=FALSE, warning=FALSE}
data <- ENROLL_OVERVIEW 

data$Time_chronological <- factor(data$Time_chronological, levels = c("Apr_2019", "May_2019", "June_2019", "Jul_2019",  "Aug_2019", "Sep_2019", "Oct_2019", "Nov_2019", "Dec_2019", "Jan_2020", "Feb_2020", "Mar_2020"))


data <- data %>% select(Time_chronological, GROUP, C_EXPECTED, C_PROJECTED, `C_ENROLLED FMRI`, `C_ENROLLED NO FMRI`, C_EXCLUDED)
data_melt <- reshape2::melt(data,  id = c("Time_chronological", "GROUP"))

#str(data_melt)


ggplot(data= data_melt, aes(x = Time_chronological, y = value, color = variable, fill = variable, group = variable)) + geom_point(stat = "summary", fun.y=sum) +  stat_summary(fun.y=sum, geom="line")  + theme(axis.text.x = element_text(angle = 45))  + scale_color_brewer(palette = "Set1")+ facet_wrap(~GROUP, ncol = 2)
  


#geom_point(stat='summary', fun.y=sum) +stat_summary(fun.y=sum, geom="line") #+ facet_wrap(~GROUP)



#View(data_melt)


#str(data)


#data$EXPECTED

```

****
<!-- # Upcoming Week -->

```{r Tally of Sessions for Current Week - UPDATE DATE WEEKLY, warning=FALSE, include=FALSE}

TALLY_UPCOMING_SESSIONS <- SCHEDULE %>% select(`First Name`, `Last Name`, `Type (Recode)`, `Calendar`, `Start Time`, `Session Date`) %>%
  dplyr::filter(SCHEDULE$`Session Date`>= START_WEEK & SCHEDULE$`Session Date` <= END_WEEK) %>%
  group_by(`Type (Recode)`) %>%
  tally() %>%
  arrange(desc(n))

knitr::kable(
  TALLY_UPCOMING_SESSIONS, 
  caption = "Upcoming Sessions (1-3 ONLY)",
  col.names = c("Session Type", "Number"))

```

***

<!-- ### Session 1 -->

```{r Enrollment Session 1s for Current Week - UPDATE DATE WEEKLY, eval=FALSE, include=FALSE}
ENROLLING<- SCHEDULE %>% select(`First Name`, `Last Name`, `Start Time`,`Start Time (AM/PM)`, `Type`, `Calendar`) %>%
dplyr::filter((`Start Time` >= as.Date("2020-01-20") & `Start Time` <= as.Date("2020-01-25")) & (`Type` == "Session 1"))

ENROLLING<- ENROLLING %>% select(-'Start Time')

knitr::kable(
  ENROLLING, 
  caption = "New Enrollment (Current Week)",
  col.names = c("First Name", "Last Name", "Date/Time", "Session", "Assigned Researcher"))


```

```{r Follow-Up Session 1s for Current Week, eval=FALSE, include=FALSE}

UPCOMMING_FU <- SCHEDULE %>% select(`First Name`, `Last Name`, `Start Time`, `Type`, `Calendar`) %>%
dplyr::filter((`Start Time` >= as.Date("2019-11-04") & `Start Time` <= as.Date("2019-11-11")) & (`Type` == "Session 1 Follow Up (1.5 hours)" | `Type` == "Session 1 Follow Up (30 minutes)" | `Type` == "Session 1 Follow Up (3 hours)"))

knitr::kable(
  UPCOMMING_FU, 
  caption = "Follow-Up Sessions Scheduled This Week",
  col.names = c("First Name", "Last Name", "Date", "Session", "Assigned Researcher"))
```

<!-- ### Session 2 -->

```{r Session 2 For Current Week - UPDATE DATE WEEKLY, eval=FALSE, include=FALSE}
SESSION_2 <- SCHEDULE %>% select(`First Name`, `Last Name`,`Session Date`, `Type`, `Calendar`) %>%
dplyr::filter((SCHEDULE$`Session Date`>= START_WEEK & SCHEDULE$`Session Date` <= END_WEEK) & (`Type` == "Session 2"))

knitr::kable(
  SESSION_2, 
  caption = "Upcoming Session 2 (Current Week)",
  col.names = c("First Name", "Last Name", "Date", "Session", "Assigned Researcher"))

```

<!-- ### Session 3 -->

```{r Session 3 For Current Week, eval=FALSE, include=FALSE}
SESSION_3 <- SCHEDULE %>% select(`First Name`, `Last Name`, `Session Date`, `Type (Recode)`, `Calendar`) %>%
dplyr::filter((SCHEDULE$`Session Date`>= START_WEEK & SCHEDULE$`Session Date` <= END_WEEK) & (`Type (Recode)` == "Session 3") | (`Type (Recode)` == "Session 3 FU"))

knitr::kable(
  SESSION_3, 
  caption = "Upcoming Session 3 (Current Week)",
  col.names = c("First Name", "Last Name", "Date", "Session", "Assigned Researcher"))
```

<!-- ### Session 4 -->

```{r Current Week Session 4, eval=FALSE, include=FALSE}

knitr::kable(
  TRACKER %>% select(ID, NAME, S4_DATE) %>%
  dplyr::filter(S4_DATE >= START_WEEK & S4_DATE <= END_WEEK), 
  caption = "Upcoming Session 4 (Current Week)",
  col.names = c("ID", "Name", "Date"))
  

```

<!-- ## All Future Sessions -->

```{r Sessions for the Following Week, eval=FALSE, include=FALSE}
#all upcomming sessions - i took this off this week because its too much data
#MUST CHANGE DATE
UPCOMMING_ALL <- SCHEDULE %>% select(`First Name`, `Last Name`, `Start Time`, `Type`, `Calendar`) %>%
dplyr::filter(`Start Time` >= as.Date("2019-11-11") & `Start Time` <= as.Date("2019-11-30"))
# 
knitr::kable(
UPCOMMING_ALL, 
  caption = "Sessions for the Following Week",
  col.names = c("First Name", "Last Name", "Date", "Session", "Assigned Researcher"))

```

<!-- ## Past Week Sessions -->
```{r Sessions Last Week, eval=FALSE, include=FALSE}
#MUST CHANGE DATE
LASTWEEK <- SCHEDULE %>% select(`First Name`, `Last Name`, `Start Time`, `Type`, `Calendar`) %>%
dplyr::filter(`Start Time` >= as.Date("2019-10-27") & `Start Time` <= as.Date("2019-11-03"))


knitr::kable(
  LASTWEEK, 
  caption = "Sessions Scheduled Last Week",
  col.names = c("First Name", "Last Name", "Date", "Session", "Assigned Researcher"))
```

```{r Session 1 Notes, eval=FALSE, include=FALSE}
## Session 1 Notes - should be caption when working

s1 <- read_csv(paste0(directory,"S1+Check+List_October+14,+2019_12.12 (1).csv"), col_names = TRUE) %>% 
  #, col_types = cols(
  # "Recorded Date" = col_datetime(format = "%Y-%m-%d %H:%M:%S"))) %>%
#filter("Response Type" == "IP Address")  %>% #select only real entries, filter by date
  select(Q1.1_1:Q3.6) %>% #rename
  rename(
    id ="Q1.1_4", 
    session_date = "Q1.1_1",
    session_time = "Q1.1_2", is_followup = "Q1.2", interviewer = "Q1.1_3", visit1_checklist = "Q2.1", visit1_notes = "Q2.2", session_complete = "Q2.3", followup = "Q2.4", followup_date = "Q2.5", need_followup = "Q2.6", visit2_checklist = Q3.1, visit1_makeup = Q3.2, visit1_makeuptxt = Q3.2_5_TEXT, session_complete2 = Q3.3, followup2 = Q3.4, followup_date2 = Q3.5, need_followup2 = Q3.6) %>%
   arrange(desc(session_date))

#sort items by visit 1 and visit 2
visit1<-select(s1, id, is_followup, session_date, visit1_notes, visit1_checklist,  session_complete, followup, followup_date, need_followup) %>%
  filter(is_followup == "No")

visit1.tabledata <-select(s1, id, session_date, interviewer, session_complete, visit1_notes)

knitr::kable(
  visit1.tabledata,
  caption = "Notes from Session 1",
 col.names = c("ID", "Session Date", "Interviewer", "Session Complete (Y/N)", "Visit Notes"))

```

# Recruitment Visual Overview

## Overview of Contact Outcomes

```{r Overview of Contact Outcomes, echo=FALSE}
total_status_graph <-MASTER %>% 
  select(STATUS) %>%
  dplyr::filter(!is.na(STATUS)) %>%
  group_by(STATUS) %>%
  tally()%>%
  ggplot(aes(x=reorder(STATUS,-n), y=n, fill = STATUS)) +
    geom_bar(stat="identity") +
  scale_fill_brewer("Spectral") +
    xlab("") +
    ylab("") +
    coord_flip()+ 
  theme(legend.position="none") +
  ggtitle("Activity from July 01 - Today")

#CHANGE FILTER TO CURRENT 1 WEEK PERIOD

enrollment_pastweek_visual <-MASTER %>% 
  select(STATUS, SCREEN_SENTDATE) %>%
  dplyr::filter((SCREEN_SENTDATE >= START_LWEEK & SCREEN_SENTDATE <= START_WEEK & !is.na(STATUS))) %>%
  group_by(STATUS) %>%
  tally()%>%
  ggplot(aes(x=reorder(STATUS,-n), y=n, fill = STATUS)) +
    geom_bar(stat="identity") +
  scale_fill_brewer("Spectral") +
    xlab("") +
    ylab("") +
    coord_flip() + 
  theme(legend.position="none") +
  ggtitle(ENROLL_PASTWEEK_TITLE)

plot_grid(total_status_graph, enrollment_pastweek_visual,  ncol = 1)
```

***
## Source of Study Activity (July 01- Today)

```{r Source of Inquiry and Eligibility, echo=FALSE, warning=FALSE}
inquiry_plot<-MASTER %>% select(SOURCE) %>%
  group_by(SOURCE) %>%
  tally() %>%
  arrange(desc(SOURCE)) %>%
  ggplot(aes(x=reorder(SOURCE,-n), y=n, fill = SOURCE)) +
    geom_bar(stat="identity") +
  scale_fill_brewer("Spectral") +
    xlab("") +
    ylab("Inquired About Study") +
    coord_flip()+ 
  theme(legend.position="none")


source_enrollment_plot<-MASTER %>% select(SOURCE, STATUS) %>%
  dplyr::filter(STATUS == "Invited S1") %>%
  group_by(SOURCE) %>%
  tally() %>%
  arrange(desc(SOURCE)) %>%
  ggplot(aes(x=reorder(SOURCE,-n), y=n, fill = SOURCE)) +
    geom_bar(stat="identity") +
  scale_fill_brewer("Spectral") +
    xlab("") +
    ylab("Eligible After Baseline Screen") +
    coord_flip()+ 
  theme(legend.position="none")

plot_grid(inquiry_plot, source_enrollment_plot, ncol = 2)

```

```{r Source of Contacts - Past Week, eval=FALSE, include=FALSE}
source_contacts_pastweek_graph <- MASTER %>% 
  dplyr::select(SCREEN_SENTDATE, SOURCE) %>%
  filter(SCREEN_SENTDATE >= START_LWEEK & SCREEN_SENTDATE <= START_WEEK) %>%
  ggplot(aes(SOURCE)) +
  geom_bar(aes(SOURCE, fill = SOURCE,)) +
  labs(title ="Source of Contacts (Past Week)", y = "Number of Contacts", x = "Source") + 
  theme(legend.position = "none")

```

```{r Gender Visualization, eval=FALSE, include=FALSE}
graph_INVTEDS1_TO_DATE <- TRACKER %>% dplyr::select(GENDER, GROUP) %>%
ggplot(aes(GROUP)) +
  geom_bar(aes(GROUP, fill = GENDER,)) + 
  scale_fill_manual(name = "Gender of S1 Participants",
                    values = c("pink", "blue", "black"),
                    labels = c("Female", "Male", "Unknown")) +
  labs(title ="Gender Distribution of All Participants Invited to S1 (To Date)", y = "Number", x = "Group") 

MASTER %>% dplyr::select(GENDER) %>%
ggplot(aes(GENDER)) +
  geom_bar(aes(GENDER, fill = GENDER,)) +
  labs(title ="Distribution of Gender (All Contacts)", y = "Count", x = "Gender")



#plot_grid(graph_TO_DATE, graph_WEEKLY_SOURCE, ncol = 1)


```


```{r Counts of All Contacts, eval=FALSE, include=FALSE}
#COUNTS OF ALL CONTACTS

SOURCE_COUNT<-TO_DATE %>% 
  select(SOURCE) %>%
  group_by(SOURCE) %>%
  tally()

GENDER_COUNT <-TO_DATE %>% 
  select(GENDER) %>%
  group_by(GENDER) %>%
  tally()

AGE_COUNT <- TO_DATE %>% 
  select(AGE) %>%
  group_by(AGE) %>%
  tally()

SCREEN_COMPLETE_COUNT <- TO_DATE %>% 
  select(SCREEN_COMPLETEYN) %>%
  group_by(SCREEN_COMPLETEYN) %>%
  tally()

new_df<-full_join(SOURCE_COUNT, SCREEN_COMPLETE_COUNT)
new_df_2 <-full_join(AGE_COUNT, GENDER_COUNT)
new_new <-full_join(new_df, new_df_2 )
```

***
# Visual Status of Scheduled and Enrolled Participants

```{r Age Visualization, echo=FALSE, warning=FALSE}

# graph_age_contacts <- MASTER %>% select(AGE) %>%
#   ggplot(aes(AGE)) +
#   geom_histogram(bins = 10, color = "black", fill = "lightblue") + 
#   labs(title ="Age: All Contacts To Date", y = "Number", x = "Age")  +
#   theme(plot.title = element_text(size = 10))


graph_age_enrolled_dense <- TRACKER %>%
  filter(STATUS != 'NO SHOW') %>%
  ggplot(aes(AGE)) +
geom_density(fill="#69b3a2", color="#e9ecef", alpha=.8) +
  labs(title ="Age: Scheduled and Enrolled Participants", y = "Density", x = "Age")  +
  theme(plot.title = element_text(size = 10))

graph_age_contacts_dense <- MASTER %>% select(AGE) %>%
  ggplot(aes(AGE)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=.8)+ 
  labs(title ="Age: All Contacts To Date", y = "Density", x = "Age")  +
  theme(plot.title = element_text(size = 10))

plot_grid(graph_age_enrolled_dense, graph_age_contacts_dense, nrow = 1)


```

```{r eval=FALSE, include=FALSE}

# graph_TO_DATE_GENDER <- MASTER %>%
# ggplot(aes(GENDER)) +
#   geom_bar(aes(GENDER, fill = GENDER,)) +
#   labs(title ="Gender: All Contacts To Date", y = "Count", x = "Gender") +
#   theme(plot.title = element_text(size = 10))
  
```

```{r Visual Status of Enrolled Participants, echo=FALSE}

#TRACKER[,13] <- ifelse(TRACKER[,13] == "M", 1, ifelse(A[,1] == "F", 2, 99))

#Define the number of colors you want
nb.cols <- 18
mycolors <- colorRampPalette(brewer.pal(8, "Set2"))(nb.cols)


status_graph<-TRACKER %>% select(STATUS) %>%
  #dplyr::filter(str_detect(STATUS, "L$"))
  tally() %>%
  arrange(n) %>%
  ggplot(aes(x=STATUS, y=n, fill = STATUS)) + 
  geom_bar(stat = "identity") +
  theme_minimal() +
  coord_flip()+ 
  labs(title ="Participant Pipeline Summary", x = "Status", y = "Number") +
  theme(legend.position="none")

graph_S1_GENDERGROUP <- TRACKER %>%
  dplyr::filter(GROUP != "Ineligible") %>%
  ggplot(aes(GROUP)) +
  geom_bar(aes(GROUP, fill = GENDER,))  +
 labs(title ="Gender: Scheduled or Enrolled Participants by Diagnostic Group", y = "Number") +
  theme(plot.title = element_text(size = 10),
        axis.title = element_text(size = 8)) +
  scale_fill_manual(values = c("pink", "blue")) +
   theme(legend.position="none")

graph_S1_GENDER <- TRACKER %>%
  ggplot(aes(GENDER)) +
  geom_bar(aes(GENDER, fill = GENDER,)) +
  labs(title ="Gender: Scheduled or Enrolled Participants", y = "Count", x = "Gender")  +
  theme(plot.title = element_text(size = 10)) +
  scale_fill_manual(values = c("pink", "blue")) +
  theme(legend.position="none")


plot_grid(graph_S1_GENDER, graph_S1_GENDERGROUP, nrow = 1)

```

<!-- ### Age and Gender Breakdown -->

```{r eval=FALSE, include=FALSE}
plot_grid(graph_age_enrolled_dense, graph_S1_GENDER, ncol = 1)
```


```{r echo=FALSE}
TRACKER %>%
  mutate(NEW_VAR=case_when(
    .$STATUS == "Scheduled S1" ~ "S1",
    .$STATUS == "Canceled S1" ~ "NOT ENROLLED",
    .$STATUS == "Scheduled S1 FU" ~ "S1",
    .$STATUS == "Completed S1" ~ "STUCK",
    .$STATUS == "Scheduled S2" ~ "S2",
    .$STATUS == "Completed S2" ~ "STUCK",
    .$STATUS == "Scheduled S3, Scheduled S4" ~ "S3/S4",
    .$STATUS == "Scheduled S3" ~ "S3",
    .$STATUS == "S3 Not Completed" ~ "STUCK",
    .$STATUS == "Completed S3" & .$R01_ENROLLMENT == "Y" ~ "SCAN NEEDED",
    .$STATUS == "Completed S3" & .$R01_ENROLLMENT == "N" ~ "NO FMRI - COMPLETED T1",
    .$STATUS == "Scheduling S4" ~ "SCHEDULING",
    .$STATUS == "Invited S3" ~ "SCHEDULING",
    .$STATUS == "Ineligible" ~ "INEL",
    .$STATUS == "Non Responsive" ~ "NR",
    .$STATUS == "Completed S4" ~ "FMRI - COMPLETED T1",
    .$STATUS == "Non Responsive/Missed Session/Stuck" ~ "STUCK",
    .$STATUS == "Scheduled S4" ~ "S4",
    .$STATUS == "Scheduled S3, Completed S4" ~ "S3 SCHEDULED, S4 COMPLETED",
    .$STATUS == "Excluded" ~ "INEL",
    .$`STUDY PROGRESS` == "MIA" ~ "MIA")
  ) %>%
  select(NEW_VAR) %>%
  drop_na()%>%
  dplyr::filter(!NEW_VAR %in% c("NR", "INEL")) %>%
  ggplot(aes(x=NEW_VAR)) +
  geom_bar(stat="count")
       
```


