---
title: "Weekly Recruitment Check"
subtitle: 
author: 
date: 10/14/19
output:
  html_document:
    code_folding: hide
    df_print: kable
    mathjax: default
    number_sections: no
    theme: spacelab
    toc: yes
    toc_depth: 3
    fig_width: 9 
    fig_height: 6 
  pdf_document:
    code_folding: hide
    df_print: kable
    number_sections: yes
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Packages, include=FALSE}
library(readxl)
library(cowplot)
library(qualtRics)
library(readxl)
library(skimr)
library(tidyverse)
library(lubridate)

```


```{r Import + Clean Data for Enrollment Master, include=FALSE}
#setwd("Box Sync/DEPENd/NeuroMAP/Recruitment/Participant Management/")
directory<-file.path("/Users/bbh5255/Box Sync/DEPENd/NeuroMAP/Recruitment/Participant Management/") #set personal directory

#read in data for master file spreadsheet and R01 information - REMOVE PASSWORD FROM MASTER
MASTER <- read_xlsx(paste0(directory, "NEUROMAP Master V2.xlsx"), sheet = "MasterData")
ENROLL_OVERVIEW <- read_xlsx(paste0(directory, "NEUROMAP Master V2.xlsx"), sheet = "RO1 Aggregate", col_names = TRUE)
ENROLL_MASTER <- read_xlsx(paste0(directory, "NEUROMAP Master V2.xlsx"), sheet = "Tracker")
SCHEDULE <-read_csv(paste0(directory, "schedule2019-09-29.csv")) #read in acuity schedule info

#tidy up column names for MASTER

MASTER<-dplyr::rename(MASTER, PAI= "PAI (M)", AI = "AI (M)", SH = "SH (M)", SPIN = "SPIN (M)", SCREEN_SENTDATE = "SCREEN: SENT DATE (M)", SCREEN_COMPLETEDATE = "SCREEN: COMPLETE DATE (M)", SCREEN_COMPLETEYN =  "SCREEN: COMPLETE Y/N (M)")
MASTER<-dplyr::rename(MASTER, INEL_CODE = "INELEGIBILITY CODE (M)", INEL_PHASE ="PHASE DEEMED INELIGIBLE (M)", INEL_YN = "ELIGIBLE YN (M)",  GROUP_SL = "GROUPED: SL (M)" )
MASTER<-dplyr::rename(MASTER, S1_DATE = "S1 DATE (M)", S2_DATE ="S2 DATE (M)", S3_DATE = "S3 DATE (M)", S4_DATE = "S4 DATE (M)", S5_DATE = "S5 DATE (M)", INVITES1_YN = "INVITED TO S1 (M)", GENDER = "GENDER (M)")

#create record of start month and year for participants
MASTER$SCREEN_SENTDATE <- as.POSIXct(strptime(MASTER$SCREEN_SENTDATE, format = '%Y-%m-%d'))
MASTER$SCREEN_COMPLETEDATE <- as.POSIXct(strptime(MASTER$SCREEN_COMPLETEDATE, format = '%Y-%m-%d'))
MASTER$S1_DATE <- as.POSIXct(strptime(MASTER$S1_DATE, format = '%Y-%m-%d'))

MASTER$SCREEN_SENT_MONTH <- format(MASTER$SCREEN_SENTDATE, '%m')
MASTER$SCREEN_SENT_YEAR <- format(MASTER$SCREEN_SENTDATE, '%Y')

MASTER$SCREEN_COMPLETE_MONTH <- format(MASTER$SCREEN_COMPLETEDATE, '%m')
MASTER$SCREEN_COMPLETE_YEAR <- format(MASTER$SCREEN_COMPLETEDATE, '%Y')

MASTER$S1_MONTH <- format(MASTER$S1_DATE, '%m')
MASTER$S1_YEAR <- format(MASTER$SCREEN_COMPLETEDATE, '%Y')

#factorize source

MASTER$STATUS <-factor(MASTER$STATUS, levels = c("Completed S2", "Completed screen", "Inquiry", "Invited S1", "No longer interested", "Scheduled S1", "Screen sent"))
levels(MASTER$STATUS)[levels(MASTER$STATUS)=="Screen sent"] <- "Screen Sent, Not Completed"
levels(MASTER$STATUS)[levels(MASTER$STATUS)=="Completed screen"] <- "Ineligible After Screen"

# MASTER$SOURCE <- factor(MASTER$SOURCE, levels = c("Craigslist", "Facebook/Contact Form", "Flyer", "Flyer/Davey Lab", "Flyer/HUB", "Flyer/Library", "Flyer/Moore", "Flyer/On Campus", "Flyer/Willard", "Flyer/Forum Building", "StudyFinder", "Word of Mouth", "Unknown"))
MASTER$SOURCE[is.na(MASTER$SOURCE)] <- "Unknown"

#clean variables in enrollment master
ENROLL_MASTER <- ENROLL_MASTER %>% rename(S1_DATE = "S1 DATE", S2_DATE = "S2 DATE", S3_DATE = "S3 DATE", S4_DATE = "S4 DATE", S5_DATE = "S5 DATE", R01_ENROLLMENT = "FMRI GROUP (Y/N)")

MASTER$NAME<-gsub("(?<=[A-Z])[^A-Z]+", "", MASTER$NAME, perl = TRUE) # remove names and make initials
ENROLL_MASTER$NAME<-gsub("(?<=[A-Z])[^A-Z]+", "", ENROLL_MASTER$NAME, perl = TRUE) # remove names and make initials ENROLL_MASTER

ENROLL_MASTER$`S1 FU 1`<- as_date(ENROLL_MASTER$`S1 FU 1`)

#convert date time to readable format in R, strip time
SCHEDULE$`Start Time`<-as.Date(parse_datetime(SCHEDULE$`Start Time`, "%B %d, %Y %H:%M %p", locale=locale(tz = "US/Eastern")))

```

```{r eval=FALSE, include=FALSE}
ACUITY<-read_csv(paste0(directory, "schedule2019-10-14.csv"))
colnames(ACUITY)  

#tota number of appointments that are not canceled/no-show by person
ACUITY %>% select(Calendar, Canceled) %>%
  filter(is.na(Canceled)) %>%
  group_by(Calendar) %>%
  tally()

ACUITY %>% select(Calendar, Canceled, Type) %>%
  filter(is.na(Canceled)) %>%
  group_by(Calendar, Type) %>%
  tally() 

     
```



```{r Import Qualtrics Data, eval=FALSE, include=FALSE}

q_token <- "bigsHycE1tmf2sfK5HR2CKShxGPasXZqC2QZ2Gvl" #Begonias Account
qualtrics_api_credentials(api_key = q_token, 
                          base_url = "pennstate.ca1.qualtrics.com",
                          install = FALSE)
surveys<-all_surveys()
S1_Checklist<-fetch_survey(surveyID = surveys$id[12] , label=FALSE, verbose = TRUE, convert = TRUE,)

```

# Enrollment Overview

## RO1 Enrollment Targets For September

```{r RO1 Enrollment Overview, echo=FALSE}

#Totals for the month

SEPT_RO1 <-ENROLL_OVERVIEW %>%
  select(YEAR, MONTH, GROUP, EXPECTED, PROJECTED, `ENROLLED FMRI`, `ENROLLED NO FMRI`, `TOTAL EXCLUDED`, C_EXPECTED) %>%
    filter(MONTH == 10 & YEAR == 1) 

SEPT_RO1 <-SEPT_RO1 %>%
  select(GROUP, EXPECTED, PROJECTED, `ENROLLED FMRI`, `ENROLLED NO FMRI`,`TOTAL EXCLUDED` )

knitr::kable(
  SEPT_RO1, 
  caption = "October R01 Enrollment Targets",
  col.names = c("Diagnostic Group", "Expected Enrollment to Fulfill R01 Timeline in the Month of October", "In Process of Enrollment", "Enrolled in FMRI Group", "Not Enrolled in FMRI Group/Unassigned", "Excluded"))

```

### Overview of Enrollment To Date

```{r echo=FALSE}
#TOTAL TO DATE

RO1_TOTAL <-ENROLL_OVERVIEW %>%
  #select(YEAR, MONTH, GROUP,  C_EXPECTED, `C_ENROLLED FMRI`,`C_ENROLLED NO FMRI`,C_EXCLUDED,C_PROJECTED ) %>%
    dplyr::filter(MONTH == 10 & YEAR) %>%
  group_by(GROUP)

RO1_TOTAL <-select(RO1_TOTAL, GROUP, C_EXPECTED, C_PROJECTED, `C_ENROLLED FMRI`,`C_ENROLLED NO FMRI`, C_EXCLUDED)

knitr::kable(
  RO1_TOTAL,
  caption = "Cummulative R01 Enrollment To Date (Aug - Oct)",
  col.names = c("Diagnostic Group", "Cumulative Expected Enrollment to Fulfill R01 Timeline", "In Process of Enrollment", "Enrolled in FMRI Group", "Not Enrolled in FMRI Group/Unassigned", "Excluded"))

```

# Time Series

```{r}
data <- ENROLL_OVERVIEW 

data$Time_chronological <- factor(data$Time_chronological, levels = c("Apr_2019", "May_2019", "June_2019", "Jul_2019",  "Aug_2019", "Sep_2019", "Oct_2019", "Nov_2019", "Dec_2019", "Jan_2020", "Feb_2020", "Mar_2020"))


data <- data %>% select(Time_chronological, GROUP, C_EXPECTED, C_PROJECTED, `C_ENROLLED FMRI`, `C_ENROLLED NO FMRI`, C_EXCLUDED)
data_melt <- reshape2::melt(data,  id = c("Time_chronological", "GROUP"))

str(data_melt)


ggplot(data= data_melt, aes(x = Time_chronological, y = value, color = variable, fill = variable, group = variable)) + geom_point(stat = "summary", fun.y=sum) +  stat_summary(fun.y=sum, geom="line")  + theme(axis.text.x = element_text(angle = 45))  + scale_color_brewer(palette = "Set1")+ facet_wrap(~GROUP, ncol = 2)
  


#geom_point(stat='summary', fun.y=sum) +stat_summary(fun.y=sum, geom="line") #+ facet_wrap(~GROUP)



View(data_melt)


str(data)


data$EXPECTED

```



# Session Overview

## Upcoming Week

```{r Tally of Sessions for Current Week - UPDATE DATE WEEKLY , echo=FALSE}

TALLY_UPCOMING_SESSIONS <- SCHEDULE %>% select(`First Name`, `Last Name`, `Start Time`, `Type`, `Calendar`) %>%
  dplyr::filter(`Start Time` >= as.Date("2019-10-14") & `Start Time` <= as.Date("2019-10-21")) %>%
  group_by(`Type`) %>%
  tally() %>%
  arrange(desc(n))

knitr::kable(
  TALLY_UPCOMING_SESSIONS, 
  caption = "",
  col.names = c("Session Type", "Number"))

```

### Session 1
```{r Enrollment Session 1s for Current Week - UPDATE DATE WEEKLY, echo=FALSE}
ENROLLING<- SCHEDULE %>% select(`First Name`, `Last Name`, `Start Time`, `Type`, `Calendar`) %>%
dplyr::filter((`Start Time` >= as.Date("2019-10-21") & `Start Time` <= as.Date("2019-10-21")) & (`Type` == "Session 1"))

knitr::kable(
  ENROLLING, 
  caption = "New Enrollment (Current Week)",
  col.names = c("First Name", "Last Name", "Date", "Session", "Assigned Researcher"))
```

```{r Follow-Up Session 1s for Current Week - UPDATE DATE WEEKLY, echo=FALSE}

UPCOMMING_FU <- SCHEDULE %>% select(`First Name`, `Last Name`, `Start Time`, `Type`, `Calendar`) %>%
dplyr::filter((`Start Time` >= as.Date("2019-10-14") & `Start Time` <= as.Date("2019-10-21")) & (`Type` == "Session 1 Follow Up (1.5 hours)" | `Type` == "Session 1 Follow Up (30 minutes)" | `Type` == "Session 1 Follow Up (3 hours)"))

knitr::kable(
  UPCOMMING_FU, 
  caption = "Follow-Up Sessions Scheduled This Week",
  col.names = c("First Name", "Last Name", "Date", "Session", "Assigned Researcher"))
```

### Session 2
```{r Session 2 For Current Week - UPDATE DATE WEEKLY, echo=FALSE}
SESSION_2 <- SCHEDULE %>% select(`First Name`, `Last Name`, `Start Time`, `Type`, `Calendar`) %>%
dplyr::filter((`Start Time` >= as.Date("2019-10-14") & `Start Time` <= as.Date("2019-10-21")) & (`Type` == "Session 2"))

knitr::kable(
  SESSION_2, 
  caption = "Upcoming Session 2 (Current Week)",
  col.names = c("First Name", "Last Name", "Date", "Session", "Assigned Researcher"))

```

### Session 3
```{r Session 3 For Current Week - UPDATE DATE WEEKLY, echo=FALSE}
SESSION_3 <- SCHEDULE %>% select(`First Name`, `Last Name`, `Start Time`, `Type`, `Calendar`) %>%
dplyr::filter((`Start Time` >= as.Date("2019-10-07") & `Start Time` <= as.Date("2019-10-14")) & (`Type` == "Session 3"))

knitr::kable(
  SESSION_3, 
  caption = "Upcoming Session 3 (Current Week)",
  col.names = c("First Name", "Last Name", "Date", "Session", "Assigned Researcher"))
```

## All Future Sessions

```{r Sessions for the Following Week, echo=FALSE}
#all upcomming sessions - i took this off this week because its too much data
#MUST CHANGE DATE
UPCOMMING_ALL <- SCHEDULE %>% select(`First Name`, `Last Name`, `Start Time`, `Type`, `Calendar`) %>%
dplyr::filter(`Start Time` >= as.Date("2019-10-14") & `Start Time` <= as.Date("2019-10-21"))
# 
knitr::kable(
UPCOMMING_ALL, 
  caption = "Sessions for the Following Week",
  col.names = c("First Name", "Last Name", "Date", "Session", "Assigned Researcher"))

```

## Past Week Sessions
```{r Sessions Last Week, echo=FALSE}
#MUST CHANGE DATE
LASTWEEK <- SCHEDULE %>% select(`First Name`, `Last Name`, `Start Time`, `Type`, `Calendar`) %>%
dplyr::filter(`Start Time` >= as.Date("2019-10-07") & `Start Time` <= as.Date("2019-10-13"))


knitr::kable(
  LASTWEEK, 
  caption = "Sessions Scheduled Last Week",
  col.names = c("First Name", "Last Name", "Date", "Session", "Assigned Researcher"))
```

```{r Session 1 Notes, eval=FALSE, include=FALSE}
## Session 1 Notes - should be caption when working

s1 <- read_csv(paste0(directory,"S1+Check+List_October+14,+2019_12.12 (1).csv"), col_names = TRUE) %>% 
  #, col_types = cols(
  # "Recorded Date" = col_datetime(format = "%Y-%m-%d %H:%M:%S"))) %>%
#filter("Response Type" == "IP Address")  %>% #select only real entries, filter by date
  select(Q1.1_1:Q3.6) %>% #rename
  rename(id ="Q1.1_4", session_date = "Q1.1_1", session_time = "Q1.1_2", is_followup = "Q1.2", interviewer = "Q1.1_3", visit1_checklist = "Q2.1", visit1_notes = "Q2.2", session_complete = "Q2.3", followup = "Q2.4", followup_date = "Q2.5", need_followup = "Q2.6", visit2_checklist = Q3.1, visit1_makeup = Q3.2, visit1_makeuptxt = Q3.2_5_TEXT, session_complete2 = Q3.3, followup2 = Q3.4, followup_date2 = Q3.5, need_followup2 = Q3.6) %>%
   arrange(desc(session_date))

#sort items by visit 1 and visit 2
visit1<-select(s1, id, is_followup, session_date, visit1_notes, visit1_checklist,  session_complete, followup, followup_date, need_followup) %>%
  filter(is_followup == "No")

visit1.tabledata <-select(s1, id, session_date, interviewer, session_complete, visit1_notes)

knitr::kable(
  visit1.tabledata,
  caption = "Notes from Session 1",
 col.names = c("ID", "Session Date", "Interviewer", "Session Complete (Y/N)", "Visit Notes"))

```

# Recruitment Visual Overview

## Overview of Contact Outcomes

```{r Overview of Contact Outcomes, echo=FALSE}
total_status_graph <-MASTER %>% 
  select(STATUS) %>%
  dplyr::filter(!is.na(STATUS)) %>%
  group_by(STATUS) %>%
  tally()%>%
  ggplot(aes(x=reorder(STATUS,-n), y=n, fill = STATUS)) +
    geom_bar(stat="identity") +
  scale_fill_brewer("Spectral") +
    xlab("") +
    ylab("") +
    coord_flip()+ 
  theme(legend.position="none") +
  ggtitle("Activity from July 01 - Today")

#CHANGE FILTER TO CURRENT 1 WEEK PERIOD

enrollment_pastweek_visual <-MASTER %>% 
  select(STATUS, SCREEN_SENTDATE) %>%
  dplyr::filter((SCREEN_SENTDATE >= as.Date("2019-10-07") & SCREEN_SENTDATE <= as.Date("2019-10-14") & !is.na(STATUS))) %>%
  group_by(STATUS) %>%
  tally()%>%
  ggplot(aes(x=reorder(STATUS,-n), y=n, fill = STATUS)) +
    geom_bar(stat="identity") +
  scale_fill_brewer("Spectral") +
    xlab("") +
    ylab("") +
    coord_flip() + 
  theme(legend.position="none") +
  ggtitle("Activity from Past Week (October 7th - October 14th)")

plot_grid(total_status_graph, enrollment_pastweek_visual,  ncol = 1)
```

## Source of Study Activity (July 01- Today)

```{r Source of Inquiry and Eligibility, echo=FALSE}
inquiry_plot<-MASTER %>% select(SOURCE) %>%
  group_by(SOURCE) %>%
  tally() %>%
  arrange(desc(SOURCE)) %>%
  ggplot(aes(x=reorder(SOURCE,-n), y=n, fill = SOURCE)) +
    geom_bar(stat="identity") +
  scale_fill_brewer("Spectral") +
    xlab("") +
    ylab("Inquired About Study") +
    coord_flip()+ 
  theme(legend.position="none")


source_enrollment_plot<-MASTER %>% select(SOURCE, STATUS) %>%
  dplyr::filter(STATUS == "Invited S1") %>%
  group_by(SOURCE) %>%
  tally() %>%
  arrange(desc(SOURCE)) %>%
  ggplot(aes(x=reorder(SOURCE,-n), y=n, fill = SOURCE)) +
    geom_bar(stat="identity") +
  scale_fill_brewer("Spectral") +
    xlab("") +
    ylab("Eligible After Baseline Screen") +
    coord_flip()+ 
  theme(legend.position="none")

plot_grid(inquiry_plot, source_enrollment_plot, ncol = 2)

```

```{r Source of Contacts - Past Week, eval=FALSE, include=FALSE}
source_contacts_pastweek_graph <- MASTER %>% 
  dplyr::select(SCREEN_SENTDATE, SOURCE) %>%
  filter(SCREEN_SENTDATE >= as.Date("2019-10-07") & SCREEN_SENTDATE <= as.Date("2019-10-14")) %>%
  ggplot(aes(SOURCE)) +
  geom_bar(aes(SOURCE, fill = SOURCE,)) +
  labs(title ="Source of Contacts (Past Week)", y = "Number of Contacts", x = "Source") + 
  theme(legend.position = "none")

```

```{r Gender Visualization, eval=FALSE, include=FALSE}
graph_INVTEDS1_TO_DATE <- ENROLL_MASTER %>% dplyr::select(GENDER, GROUP) %>%
ggplot(aes(GROUP)) +
  geom_bar(aes(GROUP, fill = GENDER,)) + 
  scale_fill_manual(name = "Gender of S1 Participants",
                    values = c("pink", "blue", "black"),
                    labels = c("Female", "Male", "Unknown")) +
  labs(title ="Gender Distribution of All Participants Invited to S1 (To Date)", y = "Number", x = "Group") 

MASTER %>% dplyr::select(GENDER) %>%
ggplot(aes(GENDER)) +
  geom_bar(aes(GENDER, fill = GENDER,)) +
  labs(title ="Distribution of Gender (All Contacts)", y = "Count", x = "Gender")



#plot_grid(graph_TO_DATE, graph_WEEKLY_SOURCE, ncol = 1)


```


```{r Counts of All Contacts, eval=FALSE, include=FALSE}
#COUNTS OF ALL CONTACTS

SOURCE_COUNT<-TO_DATE %>% 
  select(SOURCE) %>%
  group_by(SOURCE) %>%
  tally()

GENDER_COUNT <-TO_DATE %>% 
  select(GENDER) %>%
  group_by(GENDER) %>%
  tally()

AGE_COUNT <- TO_DATE %>% 
  select(AGE) %>%
  group_by(AGE) %>%
  tally()

SCREEN_COMPLETE_COUNT <- TO_DATE %>% 
  select(SCREEN_COMPLETEYN) %>%
  group_by(SCREEN_COMPLETEYN) %>%
  tally()

new_df<-full_join(SOURCE_COUNT, SCREEN_COMPLETE_COUNT)
new_df_2 <-full_join(AGE_COUNT, GENDER_COUNT)
new_new <-full_join(new_df, new_df_2 )
```

# Visual Status of Scheduled and Enrolled Participants

```{r Age Visualization, echo=FALSE, warning=FALSE}

# graph_age_contacts <- MASTER %>% select(AGE) %>%
#   ggplot(aes(AGE)) +
#   geom_histogram(bins = 10, color = "black", fill = "lightblue") + 
#   labs(title ="Age: All Contacts To Date", y = "Number", x = "Age")  +
#   theme(plot.title = element_text(size = 10))


graph_age_enrolled_dense <- ENROLL_MASTER %>%
  filter(STATUS != 'NO SHOW') %>%
  ggplot(aes(AGE)) +
geom_density(fill="#69b3a2", color="#e9ecef", alpha=.8) +
  labs(title ="Age: Scheduled and Enrolled Participants", y = "Density", x = "Age")  +
  theme(plot.title = element_text(size = 10))

graph_age_contacts_dense <- MASTER %>% select(AGE) %>%
  ggplot(aes(AGE)) +
  geom_density(fill="#69b3a2", color="#e9ecef", alpha=.8)+ 
  labs(title ="Age: All Contacts To Date", y = "Density", x = "Age")  +
  theme(plot.title = element_text(size = 10))



```

```{r eval=FALSE, include=FALSE}

# graph_TO_DATE_GENDER <- MASTER %>%
# ggplot(aes(GENDER)) +
#   geom_bar(aes(GENDER, fill = GENDER,)) +
#   labs(title ="Gender: All Contacts To Date", y = "Count", x = "Gender") +
#   theme(plot.title = element_text(size = 10))
  
```

```{r Visual Status of Enrolled Participants, echo=FALSE}

status_graph<-ENROLL_MASTER %>% select(STATUS) %>%
group_by(STATUS) %>%
  tally() %>%
  arrange(n) %>%
  ggplot(aes(x=STATUS, y=n, fill = STATUS)) + 
  geom_bar(stat = "identity") +
  scale_fill_brewer("Greens") +
  labs(title ="Participant Pipeline Summary", x = "Status", y = "Number") +
  theme(legend.position="none")


graph_S1_GENDERGROUP <- ENROLL_MASTER %>%
  dplyr::filter(GROUP != "Ineligible") %>%
  ggplot(aes(GROUP)) +
  geom_bar(aes(GROUP, fill = GENDER,))  +
 labs(title ="Gender: Scheduled or Enrolled Participants by Diagnostic Group", y = "Number") +
  theme(plot.title = element_text(size = 10),
        axis.title = element_text(size = 8)) +
  scale_fill_manual(values = c("pink", "blue")) +
   theme(legend.position="none")

graph_S1_GENDER <- ENROLL_MASTER %>%
  ggplot(aes(GENDER)) +
  geom_bar(aes(GENDER, fill = GENDER,)) +
  labs(title ="Gender: Scheduled or Enrolled Participants", y = "Count", x = "Gender")  +
  theme(plot.title = element_text(size = 10)) +
  scale_fill_manual(values = c("pink", "blue")) +
  theme(legend.position="none")


plot_grid(status_graph, graph_S1_GENDERGROUP, ncol = 1)


```

### Age and Gender Breakdown

```{r echo=FALSE}
plot_grid(graph_age_enrolled_dense, graph_S1_GENDER, ncol = 1)
```
